Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-08-18 2_SSL_NE/article/article_main.tex
added edits
more edits

M. P. Weinold$^{1,2,3}$, S. Kolesnikov$^1$, L.D. Anadon$^{1,4}$ \\
\newline
$^1$ Centre for Environment, Energy and Natural Resource Governance, Department of Land Economy, University of Cambridge, Cambridge, UK \\
$^2$ Group for Energy Systems Analysis, Department of Mechanical and Process Engineering, ETH Zurich, Zurich, Switzerland \\
$^3$ Technology Assessment Group, Paul Scherrer Institute, Villigen, Switzerland \\
$^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA

@@

To address these questions, first, we identify three sets of metrics suitable for tracking the historical progress of LED lighting technology: 1) metrics of energy efficiency of LED devices, including the total device efficiency (“lamp efficiency”) and the sub-efficiencies that describe different energy loss channels in a LED device; 2) metrics of lighting quality relevant to consumer experience, including colour rendering index (CRI) and colour temperature (CT); and 3) LED device manufacturing cost. The rationale for the choice of these metrics, along with their detailed descriptions and definitions, are discussed in Supplementary Note 2. We then trace the historical improvements in these metrics, along with associated changes in LED chip architectures, from the time of introduction of the first commercial warm white GaN-based LEDs in 2003 to 2020, the year with the most recent data available at the time of data collection. Given the proprietary nature of knowledge in the SSL industry, we collect corresponding information using a multi-method approach combining a systematic review of scientific literature and industry reports with patent analysis and a series of elite interviews \cite{tansey2009process} with eminent experts from academia, public research institutions and industry (see Methods section and Supplementary Note 3 for details). This approach allows us to identify individual innovations in white LED technology, examine their knowledge origins to discern technology spillovers among them and quantify their contributions to the overall progress in LED efficiency and consumer experience metrics based on our modeling of LED performance and spectral metrics. We further develop a bottom-up LED manufacturing cost model with process-step resolution and use it to analyze the progress in LED manufacturing cost for the “classical” GaN-based LED chip architecture with lateral current spreading shown in Panel A in \cref{fgr:chip_architecture_overview}.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=17.5cm]{figures/costmodel_results_years.pdf}
\caption{\textbf{Historical changes in LED manufacturing cost structure.} Presented cost calculations are an outcome of our cost model (see \cref{sec:methods} and (see Methods and Supplementary Note 3) for a single low-to-mid power GaN-based, classic chip, phosphor-converted white LED package, assuming an ideal factory with state-of-the-art equipment at a U.S. location. Panels A-C: Waterfall diagrams of LED manufacturing cost structure split by manufacturing process steps for years 2003, 2012 and 2020. Process steps on the horizontal axis are sequenced from left to right in the same order as in the modelled LED manufacturing process. Panel D: Cumulative manufacturing yield after each process step for years 2003, 2012 and 2020. For a graphic representation of the manufacturing process, see the diagrams in Supplementary Figures 2-6. Abbreviations: Litho – Lithographic Process, Insp. – Inspection, Depn. – Deposition, CMP - Chemical-Mechanical Planarization.}
\label{fgr:costmodel}
\end{figure}

@@

To overcome the limitations of existing literature and patent analysis, in this study we rely on a multi-method approach to data collection and analysis, augmenting information obtained from a systematic review of the primary scientific literature \cite{Haddaway_2014}, device datasheets, relevant patents, and industry publications with information gained from semi-structured interviews with experts from academia and industry, bottom-up manufacturing cost modelling, and own calculations of LED device sub-efficiencies. We then synthesize information obtained with multiple methods to track the historical progress in white LED technology over time across the three groups of metrics (see Supplementary Note 2) and identify its sources in innovation and technology spillovers. We briefly describe our approach to each method below and provide further methodological details in Supplementary Note 3.

\subsection{Systematic Literature Review}

We collected data on LED performance and characteristics in a systematic literature review that included scientific publications, patents, conference proceedings from the largest semiconductor and optoelectronics conferences, industry periodicals and roadmaps, as well as company presentations and reports. This review was structured around the three main goals: 1) tracking the evolution of LED technology over time as indicated by three groups of progress metrics; 2) identifying individual innovations that contributed to this evolution, and quantifying their impact on device performance and manufacturing cost; and 3) determining whether these innovations had originated within the LED technology domain, or in a field of science or technology outside of SSL, making them involved in technology spillovers.

@@

\section{Acknowledgements}

>>>>

M.P. Weinold$^{1,2,3}$, S. Kolesnikov$^1$, L.D. Anadon$^{1,4}$ \\
\newline
$^1$ Centre for Environment, Energy and Natural Resource Governance, Department of Land Economy, University of Cambridge, Cambridge, UK \\
$^2$ Group for Energy Systems Analysis, Department of Mechanical and Process Engineering, ETH Zurich, Zurich, Switzerland \\
$^3$ Technology Assessment Group, Paul Scherrer Institute, Villigen, Switzerland \\
$^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA

@@

To address these questions, first, we identify three sets of metrics suitable for tracking the historical progress of LED lighting technology: 1) metrics of energy efficiency of LED devices, including the total device efficiency (“lamp efficiency”) and the sub-efficiencies that describe different energy loss channels in a LED device; 2) metrics of lighting quality relevant to consumer experience, including colour rendering index (CRI) and colour temperature (CT); and 3) LED device manufacturing cost. The rationale for the choice of these metrics, along with their detailed descriptions and definitions, are discussed in Supplementary Note 2. We then trace the historical improvements in these metrics, along with associated changes in LED chip architectures, from the time of introduction of the first commercial warm white GaN-based LEDs in 2003 to 2020, the year with the most recent data available at the time of data collection. Given the proprietary nature of knowledge in the SSL industry, we collect corresponding information using a multi-method approach combining a comprehensive review of scientific literature and industry reports with patent analysis and a series of elite interviews \cite{tansey2009process} with eminent experts from academia, public research institutions and industry (see Methods section and Supplementary Note 3 for details). This approach allows us to identify individual innovations in white LED technology, examine their knowledge origins to discern technology spillovers among them and quantify their contributions to the overall progress in LED efficiency and consumer experience metrics based on our modeling of LED performance and spectral metrics. We further develop a bottom-up LED manufacturing cost model with process-step resolution and use it to analyze the progress in LED manufacturing cost for the “classical” GaN-based LED chip architecture with lateral current spreading shown in Panel A in \cref{fgr:chip_architecture_overview}.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=17.5cm]{figures/costmodel_results_years.pdf}
\caption{\textbf{Historical changes in LED manufacturing cost structure.} Presented cost calculations are an outcome of our cost model (see \cref{sec:methods} and Supplementary Note 3) for a single low-to-mid power GaN-based, classic chip, phosphor-converted white LED package, assuming an ideal factory with state-of-the-art equipment at a U.S. location. Panels A-C: Waterfall diagrams of LED manufacturing cost structure split by manufacturing process steps for years 2003, 2012 and 2020. Process steps on the horizontal axis are sequenced from left to right in the same order as in the modelled LED manufacturing process. Panel D: Cumulative manufacturing yield after each process step for years 2003, 2012 and 2020. For a graphic representation of the manufacturing process, see the diagrams in Supplementary Figures 2-6. Abbreviations: Litho – Lithographic Process, Insp. – Inspection, Depn. – Deposition, CMP - Chemical-Mechanical Planarization.}
\label{fgr:costmodel}
\end{figure}

@@

To overcome the limitations of existing literature and patent analysis, in this study we rely on a multi-method approach to data collection and analysis, augmenting information obtained from a comprehensive review of the primary scientific literature \cite{Haddaway_2014}, device datasheets, relevant patents, and industry publications with information gained from semi-structured interviews with experts from academia and industry, bottom-up manufacturing cost modelling, and own calculations of LED device sub-efficiencies. We then synthesize information obtained with multiple methods to track the historical progress in white LED technology over time across the three groups of metrics (see Supplementary Note 2) and identify its sources in innovation and technology spillovers. We briefly describe our approach to each method below and provide further methodological details in Supplementary Note 3.

\subsection{Comprehensive Literature Review}

We collected data on LED performance and characteristics in a comprehensive literature review that included scientific publications, patents, conference proceedings from the largest semiconductor and optoelectronics conferences, industry periodicals and roadmaps, as well as company presentations and reports. This review was structured around the three main goals: 1) tracking the evolution of LED technology over time as indicated by three groups of progress metrics; 2) identifying individual innovations that contributed to this evolution, and quantifying their impact on device performance and manufacturing cost; and 3) determining whether these innovations had originated within the LED technology domain, or in a field of science or technology outside of SSL, making them involved in technology spillovers.

@@

\section*{Acknowledgements}

### 2023-08-18 2_SSL_NE/article/article_supplementary.tex
more edits

\begin{table}[H]
\small
    \centering
    \caption{Anonymized list of interviewed LED experts.}
    \vspace{5mm}
    \begin{tabular}{|l|l|l|l|l|}
    \hline
        \textit{\#} & \textit{Sector} & \textit{Role} & \textit{Country} & \textit{Expertise} \\ \hline
        1 & Academia & Senior researcher & UK & Epitaxy \\ \hline
        2 & Industry & Consultant, former senior researcher & USA & Device architecture \\ \hline
        3 & Industry & Consultant, former head of R\&D & Germany & Epitaxy \\ \hline
        4 & Academia & Professor & Austria & Phosphors \\ \hline
        5 & Industry & Consultant, former head of R\&D & USA & Device architecture \\ \hline
        6 & Consulting & Consultant, former senior technical advisor & USA & Device architecture \\ \hline
        7 & Academia & Professor & Germany & Phosphors \\ \hline
        8 & Government & R\&D manager & USA & Device architecture \\ \hline
        9 & Consulting & Consultant & USA & Device applications \\ \hline
        10 & Academia & Professor & France & Device physics \\ \hline
        11 & Industry & Senior scientist, former head of R\&D & USA & Device architecture \\ \hline
        12 & Industry & Principal scientist & Germany & Phosphors \\ \hline
        13 & Industry & Former head of R\&D & USA & Phosphors \\ \hline
    \end{tabular}
    \label{tab:interviews}
\end{table}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{./figures/costmodel.pdf}
    \caption{Schematic diagram of the cost model showing inputs to each step and computational steps leading to the cost model outputs. For the description of cost variables, see definitions in \cref{eqn:cost_wafer}. For the computation of total cost, see \cref{subsec:cost_computation}. For the computation of changes in total cost, see \cref{sec:contribution_variables}.}
    \label{fig:costmodel-schematic}
\end{figure}

>>>>

\begin{table}[H]
\small
    \centering
    \caption{Anonymized list of interviewed LED experts.}
    \vspace{5mm}
    \begin{tabular}{|l|l|l|l|l|}
    \hline
        \textit{\#} & \textit{Sector} & \textit{Role} & \textit{Country} & \textit{Area of Expertise} \\ \hline
        1 & Academia & Senior researcher & UK & Epitaxy \\ \hline
        2 & Industry & Consultant, former senior researcher & USA & Device architecture \\ \hline
        3 & Industry & Consultant, former head of R\&D & Germany & Epitaxy \\ \hline
        4 & Academia & Professor & Austria & Phosphors \\ \hline
        5 & Industry & Consultant, former head of R\&D & USA & Device architecture \\ \hline
        6 & Consulting & Consultant, former senior technical advisor & USA & Device architecture \\ \hline
        7 & Academia & Professor & Germany & Phosphors \\ \hline
        8 & Government & R\&D manager & USA & Device architecture \\ \hline
        9 & Consulting & Consultant & USA & Device applications \\ \hline
        10 & Academia & Professor & France & Device physics \\ \hline
        11 & Industry & Senior scientist, former head of R\&D & USA & Device architecture \\ \hline
        12 & Industry & Principal scientist & Germany & Phosphors \\ \hline
        13 & Industry & Former head of R\&D & USA & Phosphors \\ \hline
    \end{tabular}
    \label{tab:interviews}
\end{table}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{./figures/costmodel.pdf}
    \caption{\textbf{Cost model structure.} The diagram shows inputs to each step and computational steps leading to the cost model outputs. For the description of cost variables, see definitions for \cref{eqn:cost_wafer}.}
    \label{fig:costmodel-schematic}
\end{figure}
